PineAPPL: combining EW and QCD corrections\\ for fast evaluation of LHC processes

### 2020-10-13 paper/app-pineappl.tex
Address issues 3, 4, 6, 9, and 11 of the referee

\paragraph{Channels and Luminosity function.}
Sometimes it is useful to know which partons contribute the most and by how much.
This is what the subcommand \texttt{channels} shows:
\begin{verbatim}
 $ pineappl channels ATLASZHIGHMASS49FB.pineappl \
 > NNPDF31_nlo_as_0118_luxqed --limit 5
bin xmin xmax lumi  size
---+----+----+----+------+---+------+---+------+---+------+---+-----
  0  116  130  #15 27.42%  #0 27.42%  #5 24.52% #20 24.51% #30 1.30%
  1  130  150  #15 28.83%  #0 28.83%  #5 21.78% #20 21.78% #30 1.86%
  2  150  170  #15 29.87%  #0 29.82%  #5 19.63% #20 19.62% #30 2.32%
  3  170  190  #15 30.54%  #0 30.53% #20 18.17%  #5 18.13% #30 2.58%
  4  190  210   #0 31.06% #15 31.04%  #5 17.07% #20 17.04% #30 2.75%
  5  210  230   #0 31.46% #15 31.38% #20 16.27%  #5 16.24% #30 2.86%
  6  230  250   #0 31.73% #15 31.64% #20 15.66%  #5 15.62% #30 2.91%
  7  250  300   #0 32.07% #15 32.02%  #5 14.91% #20 14.86% #30 2.98%
  8  300  400   #0 32.62% #15 32.56%  #5 13.83% #20 13.81% #30 2.98%
  9  400  500  #15 33.14%  #0 33.12% #20 12.89%  #5 12.87% #30 2.93%
 10  500  700   #0 33.71% #15 33.31% #20 12.28%  #5 12.26% #30 2.93%
 11  700 1000  #15 34.08%  #0 33.71% #20 11.59%  #5 11.51% #30 3.06%
 12 1000 1500   #0 33.95% #15 33.88% #20 11.12%  #5 10.88% #30 3.56%
\end{verbatim}
The first three columns are known from \texttt{convolute}.
The next columns (the switch \texttt{-{}-limit 5} limits the output to five columns) show first the channel index and then the relative size of the corresponding contribution.
Since the contribution of a partonic channel can be negative, the columns are sorted ignoring the sign of the contribution.
The first line shows that for bin 0, i.e.\ for the range $\SI{116}{\giga\electronvolt} < M_{\ell \bar{\ell}} < \SI{130}{\giga\electronvolt}$, the cross section is dominated by partonic channel \texttt{\#15} (\SI{27.42}{\percent}), following by partonic channel \texttt{\#0} with same size, then channel \texttt{\#5}, etc.
The meaning of the channel numbers is given by using the subcommand \texttt{luminosity} (only an excerpt is shown):
\begin{verbatim}
id    entry
--+------------+------------
0  1 × ( 2, -2) 1 × ( 4, -4)
5  1 × ( 1, -1) 1 × ( 3, -3)
15 1 × (-4,  4) 1 × (-2,  2)
20 1 × (-3,  3) 1 × (-1,  1)
30 1 × (22, 22)
\end{verbatim}
This shows that channel \texttt{\#0} represents the up-type quark--anti-quark contributions (shown with PDG id 2 and 4 for up and charm quarks, which have the same matrix elements), channel \texttt{\#15} is the same channel with its initial states transposed, channels \texttt{\#5} and \texttt{\#20} are the down-type quark--anti-quark channels, and channel \texttt{\#30} is the photon--photon channel.
The size of the remaining channels is smaller than the photon--photon channel.
The factors \texttt{1} are not important here, but in general they can contain CKM values and charge factors that, if kept in the squared matrix elements, would not allow for sharing a single matrix element for different quark flavours and therefore slow down the calculation.
A complete list of all channels and of their contribution to the cross section for all of the processes discussed in section~\ref{sec:results} is collected in appendix~\ref{app:lumis}.

@@

The following run card was used to produce the results shown in section~\ref{sec:dy-lepton-pair-production}.
The only difference with respect to a standard \textsc{mg5\_aMC} run is the switch \texttt{set iappl 1}, which enables to fill a \textsc{PineAPPL} grid.
For a complete set of runcards and patches see \url{https://n3pdf.github.io/pineappl}.
\begin{verbatim}
set complex_mass_scheme True
import model loop_qcd_qed_sm_Gmu
define p = p b b~
define j = p
generate p p > e+ e- [QCD QED]
output @OUTPUT@
launch @OUTPUT@
fixed_order = ON
set mz @MZ@
set ymt @YMT@
set ebeam1 3500
set ebeam2 3500
set pdlabel lhapdf
set lhaid 324900
set fixed_ren_scale True
set fixed_fac_scale True
set mur_ref_fixed @MZ@
set muf_ref_fixed @MZ@
set reweight_scale True
set ptl = 25.0
set etal = 2.5
set mll = 116
#user_defined_cut set mmllmax = 1500.0
set req_acc_FO 0.0001
set iappl 1
done
quit
\end{verbatim}

>>>>

\paragraph{Channels and Luminosity function.}
Sometimes it is useful to know which partons contribute the most and by how much.
This is what the subcommand \texttt{channels} shows:
\begin{verbatim}
 $ pineappl channels ATLASZHIGHMASS49FB.pineappl \
 > NNPDF31_nlo_as_0118_luxqed --limit 5
bin xmin xmax lumi  size
---+----+----+----+------+---+------+---+------+---+------+---+-----
  0  116  130  #15 27.42%  #0 27.42%  #5 24.52% #20 24.51% #30 1.30%
  1  130  150  #15 28.83%  #0 28.83%  #5 21.78% #20 21.78% #30 1.86%
  2  150  170  #15 29.87%  #0 29.82%  #5 19.63% #20 19.62% #30 2.32%
  3  170  190  #15 30.54%  #0 30.53% #20 18.17%  #5 18.13% #30 2.58%
  4  190  210   #0 31.06% #15 31.04%  #5 17.07% #20 17.04% #30 2.75%
  5  210  230   #0 31.46% #15 31.38% #20 16.27%  #5 16.24% #30 2.86%
  6  230  250   #0 31.73% #15 31.64% #20 15.66%  #5 15.62% #30 2.91%
  7  250  300   #0 32.07% #15 32.02%  #5 14.91% #20 14.86% #30 2.98%
  8  300  400   #0 32.62% #15 32.56%  #5 13.83% #20 13.81% #30 2.98%
  9  400  500  #15 33.14%  #0 33.12% #20 12.89%  #5 12.87% #30 2.93%
 10  500  700   #0 33.71% #15 33.31% #20 12.28%  #5 12.26% #30 2.93%
 11  700 1000  #15 34.08%  #0 33.71% #20 11.59%  #5 11.51% #30 3.06%
 12 1000 1500   #0 33.95% #15 33.88% #20 11.12%  #5 10.88% #30 3.56%
\end{verbatim}
The first three columns are known from \texttt{convolute}.
The next columns (the switch \texttt{-{}-limit 5} limits the output to five columns) show first the channel index and then the relative size of the corresponding contribution.
Since the contribution of a partonic channel can be negative, the columns are sorted ignoring the sign of the contribution.
The first line shows that for bin 0, i.e.\ for the range $\SI{116}{\giga\electronvolt} < M_{\ell \bar{\ell}} < \SI{130}{\giga\electronvolt}$, the cross section is dominated by partonic channel \texttt{\#15} (\SI{27.42}{\percent}), following by partonic channel \texttt{\#0} with same size, then channel \texttt{\#5}, etc.
The meaning of the channel numbers is given by using the subcommand \texttt{luminosity} (only an excerpt is shown):
\begin{verbatim}
id    entry
--+------------+------------
0  1 x ( 2, -2) 1 x ( 4, -4)
5  1 x ( 1, -1) 1 x ( 3, -3)
15 1 x (-4,  4) 1 x (-2,  2)
20 1 x (-3,  3) 1 x (-1,  1)
30 1 x (22, 22)
\end{verbatim}
This shows that channel \texttt{\#0} represents the up-type quark--anti-quark contributions (shown with PDG id 2 and 4 for up and charm quarks, which have the same matrix elements), channel \texttt{\#15} is the same channel with its initial states transposed, channels \texttt{\#5} and \texttt{\#20} are the down-type quark--anti-quark channels, and channel \texttt{\#30} is the photon--photon channel.
The size of the remaining channels is smaller than the photon--photon channel.
The factors \texttt{1} are not important here, but in general they can contain CKM values and charge factors that, if kept in the squared matrix elements, would not allow for sharing a single matrix element for different quark flavours and therefore slow down the calculation.
A complete list of all channels and of their contribution to the cross section for all of the processes discussed in section~\ref{sec:results} is collected in appendix~\ref{app:lumis}.

@@

The following run card was used to produce the results shown in section~\ref{sec:dy-lepton-pair-production}.
The only difference with respect to a standard \textsc{mg5\_aMC} run is the switch \texttt{set pineappl True}, which enables to fill a \textsc{PineAPPL} grid.
For a complete set of runcards and patches see \url{https://n3pdf.github.io/pineappl}.
\begin{verbatim}
set complex_mass_scheme True
import model loop_qcd_qed_sm_Gmu
define p = p b b~
define j = p
generate p p > e+ e- [QCD QED]
output @OUTPUT@
launch @OUTPUT@
fixed_order = ON
set mz @MZ@
set ymt @YMT@
set ebeam1 3500
set ebeam2 3500
set pdlabel lhapdf
set lhaid 324900
set fixed_ren_scale True
set fixed_fac_scale True
set mur_ref_fixed @MZ@
set muf_ref_fixed @MZ@
set reweight_scale True
set ptl = 25.0
set etal = 2.5
set mll = 116
#user_defined_cut set mmllmax = 1500.0
set req_acc_FO 0.0001
set pineappl True
done
quit
\end{verbatim}

### 2020-10-13 paper/sec-doublecounting.tex
Clarified that our recommendation is not the ultimate one
Address issues 3, 4, 6, 9, and 11 of the referee

The ability to perform theoretical calculations simultaneously accurate in both
the QCD and EW couplings is not sufficient to make a \emph{consistent}
comparison with experimental measurements. In this section
we formulate some
guidelines to facilitate this task. We focus on the problem of data with (partially) subtracted EW effects, which, if compared to theory predictions including them, leads to a double counting issue.

@@

A second example is related to removing EW effects from data. These can be either the full EW corrections
or just a part of them. In either case, a comparison between these data and a NLO-EW accurate simulation aimed at the extraction of some parameter would be meaningless, as some effects included in the latter
have been removed from the former. The typical example relevant for the LHC is the deconvolution of effects due to multiple-photon radiation
from light particles in the final state. This applies mostly
to processes such as neutral- or charged-current Drell--Yan, especially when electrons are considered. The problem lies in the fact that
 electrons, and to a lesser extent muons, tend to radiate photons, which are not accounted
for in QCD-only matrix elements. Thus, leptons that are measured in the detector are less energetic, and this fact is compensated for
by inverting a photon shower. The resulting dataset is e.g.\ referred to as \emph{pre-FSR} with observables defined in terms of \emph{Born-level electrons} (see e.g.\ ref.~\cite{Aad:2015auj} for its definition).
These datasets are needed for and correctly used in QCD-only PDF determinations, since the EW corrections to some DY observables can be significant, and excluding them would therefore degrade the quality of the fit.
In fits including fixed-order EW corrections the problem with this definition, besides double counting, is that the first photon emission is included exactly at the matrix-element level. The inclusion of
subsequent emission would require the matching with the QED shower, which is not yet available for general processes.

>>>>

The ability to perform theoretical calculations simultaneously accurate in both
the QCD and EW couplings is not sufficient to make a \emph{consistent}
comparison with experimental measurements. In this section
we formulate some
guidelines to facilitate this task. We focus on the problem of data with (partially) subtracted EW effects, which, if compared to theory predictions including them, leads to a double counting issue.
Our guidelines are intended to make the reader aware of an
emerging new issue, whose definitive solution remains however beyond the scope
of this work.

@@

A second example is related to removing EW effects from data. These can be either the full EW corrections
or just a part of them. In either case, a comparison between these data and a NLO-EW accurate simulation aimed at the extraction of some parameter would be meaningless, as some effects included in the latter
have been removed from the former. The typical example relevant for the LHC is the deconvolution of effects due to multiple-photon radiation
from light particles in the final state. This applies mostly
to processes such as neutral- or charged-current Drell--Yan, especially when electrons are considered. The problem lies in the fact that
 electrons, and to a lesser extent muons, tend to radiate collinear photons, which are not accounted
for in QCD-only matrix elements. Thus, leptons that are measured in the detector are less energetic, and this fact is compensated for
by inverting a photon shower. The resulting dataset is e.g.\ referred to as \emph{pre-FSR} with observables defined in terms of \emph{Born-level electrons} (see e.g.\ ref.~\cite{Aad:2015auj} for its definition).
These datasets are needed for and correctly used in QCD-only PDF determinations, since the EW corrections to some DY observables can be significant, and excluding them would therefore degrade the quality of the fit.
In fits including fixed-order EW corrections the problem with this definition, besides double counting, is that the first photon emission is included exactly at the matrix-element level. The inclusion of
subsequent emission would require the matching with the QED shower, which is not yet available for general processes.

### 2020-10-13 paper/sec-pineappl.tex
Remove indentation
Address issues 3, 4, 6, 9, and 11 of the referee

In particular, \textsc{PineAPPL} supports the following features.
\begin{itemize}
\item The inclusion of perturbative corrections (fixed-order, i.e.\ without parton-shower matching) with any given set of powers of $\alpha$, $\alphas$, in particular including combined QCD--EW corrections.
\item The support for non-coloured initial-state partons, such as photon-initiated contributions, and, more generally, arbitrary initial-state combinations, e.g.\ leptonic initial states~\cite{Bertone:2015lqa,Buonocore:2020nai}.
\item The estimate of theory uncertainties via variations of the renormalisation and factorisation scale (the electroweak coupling is assumed to be scale-independent, consistently with the most common renormalisation schemes).
\end{itemize}

On a more technical level, we point out the following additional features of \textsc{PineAPPL}.

@@

\item \textsc{PineAPPL} has been explicitly interfaced to \textsc{mg5\_aMC} (v3+)~\cite{Alwall:2014hca,Frederix:2018nkq},\footnote{A version of \textsc{mg5\_aMC} interfaced to \textsc{PineAPPL} can be downloaded from \url{https://launchpad.net/mg5amc-pineappl/trunk}, and it will be included as standard in the next \textsc{mg5\_aMC} release.} see appendix~\ref{app:sample-runcard} for an example of a runcard.
The usage of \textsc{mg5\_aMC}(v3+) + \textsc{PineAPPL} is similar to that of \textsc{mg5\_aMC}(v2) + \textsc{aMCfast} + \textsc{APPLgrid}.
While the latter toolchain proved to be sufficiently efficient for NLO QCD calculations of typical kinematic distributions (with a few bins), this is longer so when taking into account NLO EW calculations and, with more precise data, distributions that are typically more complex and have more bins.
Taking into account these two reasons, we find that the memory usage of \textsc{APPLgrid} is no longer satisfiable.
In particular, using \textsc{APPLgrid} for NLO QCD+EW\footnote{For this a modified version of \textsc{APPLgrid} was developed which added support for photon-initiated processes and EW corrections.} typically requires close to \SI{120}{\giga\byte} for high-mass Drell--Yan with 13 bins (see section~\ref{sec:dy-lepton-pair-production}).
The memory usage is substantially reduced to roughly \SI{1}{\giga\byte} after \enquote{optimisation} of the grids, i.e.\ an optimisation of the grid representation in memory.
However, this requires a two-step procedure: first, to produce an unoptimised grid in order to identify those parts where the cross section is either zero or extremely suppressed; second, after those parts are removed, to fill an optimised grid with a small number of bins.
\textsc{PineAPPL} avoids this by using a more space-efficient representation from the start. This leads to substantially faster run times, in particular for simple processes, because the grids do not need to be optimised 
and their combination is faster.

>>>>

In particular, \textsc{PineAPPL} supports the following features.
\begin{itemize}
\item The inclusion of perturbative corrections (fixed-order, i.e.\ without parton-shower matching) with any given set of powers of $\alpha$, $\alphas$, in particular including combined QCD--EW corrections.
\item The support for non-coloured initial-state partons, such as photon-initiated contributions, and, more generally, arbitrary initial-state combinations, e.g.\ leptonic initial states~\cite{Bertone:2015lqa,Buonocore:2020nai}.
\item The estimate of theory uncertainties via variations of the renormalisation and factorisation scale (the electroweak coupling is assumed to be scale-independent, consistently with the most common renormalisation schemes).
\end{itemize}
On a more technical level, we point out the following additional features of \textsc{PineAPPL}.

@@

\item \textsc{PineAPPL} has been explicitly interfaced to \textsc{mg5\_aMC} (v3+)~\cite{Alwall:2014hca,Frederix:2018nkq},\footnote{A version of \textsc{mg5\_aMC} interfaced to \textsc{PineAPPL} can be downloaded from \url{https://launchpad.net/mg5amc-pineappl/trunk}, and it will be included as standard in the next \textsc{mg5\_aMC} release.} see appendix~\ref{app:sample-runcard} for an example of a runcard.
The usage of \textsc{mg5\_aMC}(v3+) + \textsc{PineAPPL} is similar to that of \textsc{mg5\_aMC}(v2) + \textsc{aMCfast} + \textsc{APPLgrid}.
While the latter toolchain proved to be sufficiently efficient for NLO QCD calculations of typical kinematic distributions (with a few bins), this is no longer so when taking into account NLO EW calculations and, with more precise data, distributions that are typically more complex and have more bins.
Taking into account these two reasons, we find that the memory usage of \textsc{APPLgrid} is no longer satisfiable.
In particular, using \textsc{APPLgrid} for NLO QCD+EW\footnote{For this a modified version of \textsc{APPLgrid} was developed which added support for photon-initiated processes and EW corrections.} typically requires close to \SI{120}{\giga\byte} for high-mass Drell--Yan with 13 bins (see section~\ref{sec:dy-lepton-pair-production}).
The memory usage is substantially reduced to roughly \SI{1}{\giga\byte} after \enquote{optimisation} of the grids, i.e.\ an optimisation of the grid representation in memory.
However, this requires a two-step procedure: first, to produce an unoptimised grid in order to identify those parts where the cross section is either zero or extremely suppressed; second, after those parts are removed, to fill an optimised grid with a small number of bins.
\textsc{PineAPPL} avoids this by using a more space-efficient representation from the start. This leads to substantially faster run times, in particular for simple processes, because the grids do not need to be optimised 
and their combination is faster.

### 2020-10-13 paper/sec-results.tex
Address issues 3, 4, 6, 9, and 11 of the referee

The values of the relevant physical parameters are chosen as
\begin{equation}
\begin{aligned}
M_\mathrm{W} &= \SI{80.419}{\giga\electronvolt} \text{,} \quad &
M_\mathrm{Z} &= \SI{91.176}{\giga\electronvolt} \text{,} \quad &
m_\mathrm{t} &= \SI{172.5}{\giga\electronvolt} \text{,} \quad \\
\Gamma_\mathrm{W} &= \SI{2.09291}{\giga\electronvolt} \text{,} &
\Gamma_\mathrm{Z} &= \SI{2.49877}{\giga\electronvolt} \text{,} &
G_\mu &= \SI{1.16639e-5}{\per\giga\electronvolt\squared} \text{,}
\end{aligned}
\label{eq:parameters}
\end{equation}
where $M_\mathrm{Z}$, $M_\mathrm{W}$, $m_\mathrm{t}$ are the values of the Z-boson, W-boson, and
top-quark masses, respectively, $\Gamma_\mathrm{Z}$ and $\Gamma_\mathrm{W}$ are the widths of
the Z and W bosons, and $G_\mu$ is the value of the Fermi coupling. The value of the strong
coupling is chosen consistently with the PDF set, $\alphas(M_\mathrm{Z})=0.118$.

@@

\paragraph{Experimental measurements and process features.}
We select the single-differential transverse momentum distribution of the
sum of the two leptons (the \enquote{Z boson}), $p_\mathrm{T}^{\ell \bar{\ell}}$, measured by the CMS experiment at a
centre-of-mass energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}.
This measurement, which has not been included in any PDF determination so far,
shows very low experimental uncertainties (at the percent level or below).
EW corrections are therefore expected to be essential to achieve a good
description of it, and to constrain accurately the PDFs, together with
NNLO QCD corrections, which are already well
known~\cite{Boughezal:2015ded,Boughezal:2016isb,Boughezal:2016yfp,Ridder:2015dxa,Ridder:2016nkl,Gehrmann-DeRidder:2017mvr,Bizon:2019zgf}
Analogous measurements,
from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
experiments at a centre-of-mass energy of \SI{8}{\tera\electronvolt},
were partly included (upon
selection of an appropriate kinematic cut that excluded bins with large EW
corrections) in a dedicated study~\cite{Boughezal:2017nla},
in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
single LO contribution $\mathcal{O}(\alphas\alpha^2)$ and a single NLO
contribution $\mathcal{O}(\alphas^2\alpha^2)$. In the NLO QCD+EW computation,
we supplement these with another LO and NLO, which are
$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alphas\alpha^3)$;
contributions of the order $\mathcal{O}(\alpha^4)$ are not considered (see ref.~\cite{Denner:2019zfp}).
EW corrections for this process were computed in
refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum,Frederix:2018nkq}.
The process receives contributions from 101 (166) parton luminosities,
see appendix~\ref{app:lumis}.

>>>>

The values of the relevant physical parameters are chosen as
\begin{equation}
\begin{aligned}
M_\mathrm{W} &= \SI{80.419}{\giga\electronvolt} \text{,} \quad &
\Gamma_\mathrm{W} &= \SI{2.09291}{\giga\electronvolt} \text{,} &
m_\mathrm{t} &= \SI{172.5}{\giga\electronvolt} \text{,} \quad \\
M_\mathrm{Z} &= \SI{91.176}{\giga\electronvolt} \text{,} \quad &
\Gamma_\mathrm{Z} &= \SI{2.49877}{\giga\electronvolt} \text{,} &
G_\mu &= \SI{1.16639e-5}{\per\giga\electronvolt\squared} \text{,} \\
M_\mathrm{H} &= \SI{125}{\giga\electronvolt} \text{,} &
\Gamma_\mathrm{H} &= \SI{4.074680e-03}{\giga\electronvolt} \text{,}
\end{aligned}
\label{eq:parameters}
\end{equation}
where $M_\mathrm{Z}$, $M_\mathrm{W}$, $M_\mathrm{H}$, $m_\mathrm{t}$ are the values of the Z-, W-, Higgs-boson
and top-quark masses, respectively, $\Gamma_\mathrm{Z}$, $\Gamma_\mathrm{W}$, $\Gamma_\mathrm{H}$ are the widths of
the Z, W and Higgs bosons, and $G_\mu$ is the value of the Fermi coupling. The value of the strong
coupling is chosen consistently with the PDF set, $\alphas(M_\mathrm{Z})=0.118$.

@@

\paragraph{Experimental measurements and process features.}
We select the single-differential transverse momentum distribution of the
sum of the two leptons (the \enquote{Z boson}), $p_\mathrm{T}^{\ell \bar{\ell}}$, measured by the CMS experiment at a
centre-of-mass energy of \SI{13}{\tera\electronvolt}~\cite{Sirunyan:2019bzr}.
This measurement, which has not been included in any PDF determination so far,
shows very low experimental uncertainties (at the percent level or below).
EW corrections are therefore expected to be essential to achieve a good
description of it, and to constrain accurately the PDFs, together with
NNLO QCD corrections, which are already well
known~\cite{Boughezal:2015ded,Boughezal:2016isb,Boughezal:2016yfp,Ridder:2015dxa,Ridder:2016nkl,Gehrmann-DeRidder:2017mvr,Bizon:2019zgf}.
Analogous measurements,
from the ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa}
experiments at a centre-of-mass energy of \SI{8}{\tera\electronvolt},
were partly included (upon
selection of an appropriate kinematic cut that excluded bins with large EW
corrections) in a dedicated study~\cite{Boughezal:2017nla},
in the NNPDF3.1 PDF set~\cite{Ball:2017nwa} and in variants of
the CT18 PDF set~\cite{Hou:2019efy}. In the QCD computation, we consider a
single LO contribution $\mathcal{O}(\alphas\alpha^2)$ and a single NLO
contribution $\mathcal{O}(\alphas^2\alpha^2)$. In the NLO QCD+EW computation,
we supplement these with another LO and NLO, which are
$\mathcal{O}(\alpha^3)$ and $\mathcal{O}(\alphas\alpha^3)$;
contributions of the order $\mathcal{O}(\alpha^4)$ are not considered (see ref.~\cite{Denner:2019zfp}).
EW corrections for this process were computed in
refs.~\cite{Kuhn:2005az,Denner:2011vu,Hollik:2015pja,Kallweit:2015dum,Frederix:2018nkq}.
The process receives contributions from 101 (166) parton luminosities,
see appendix~\ref{app:lumis}.
